---
title: "Characteristics of COVID-19 patients"
author: "Public Health - Seattle & King County"
date: '`r Sys.Date()`'
header-includes:
  - \usepackage{booktabs}
  - \usepackage{makecell}
  - \usepackage{multirow}
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

options(knitr.kable.NA = '')
```

## Introduction

This document shows demographics and clinical aspects of COVID-19 cases who have been linked to RHINO IDs. There were 
`r format(nrow(covid_orig), big.mark = ',')` clinical encounters among `r format(length(unique(covid_orig$case_id)), big.mark = ',')` linked cases.
Of those, `r format(matched$encounters, big.mark = ',')` encounters from `r format(matched$people, big.mark = ',')` individuals were found in RHINO.


## Demographics

```{r demogs, echo=FALSE}
demogs_tot %>%
    kable() %>%
  collapse_rows(columns = 1, valign = "top") %>%
  kable_styling(bootstrap_options = c("striped"), full_width = F, position = "left")

```

## Clinical outcomes

```{r events, echo=FALSE}
clinic_tot %>%
    kable() %>%
  collapse_rows(columns = 1, valign = "top") %>%
  kable_styling(bootstrap_options = c("striped"), full_width = F, position = "left")

```

